%-------------------------
% Resume in Latex
% Author: Vi Long Tran
% LinkedIn: www.linkedin.com/in/tran-long-vi-ce/
%------------------------
%------------------------
\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\name{VI}{Long Tran}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\makecvtitle
\vspace*{-15mm}
\begin{center}\textbf{DevOps Engineer}\end{center}
\begin{center}
\setlength{\tabcolsep}{10pt}
\begin{tabular}{ c c c }
\faMobile\enspace +84 342 863 321 & \faEnvelope\enspace tranlongvi.ce@gmail.com & \faHome\enspace Ho Chi Minh, Vietnam
\end{tabular}
\setlength{\tabcolsep}{7pt}
\begin{tabular}{ c  c }
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/tran-long-vi-ce/}{in/tran-long-vi-ce} &
\faGithub\enspace \color{blue} \href{https://github.com/VI-Tran-computerEngineer}{github.com/VI-Tran-computerEngineer}
\end{tabular}
\end{center}

%----------PROFILE-----------------
\section{Profile}
{
DevOps Engineer with 2+ years of experience working in various technology fields including CI/CD, Microservices, and Embedded application developments.
Skilled in developing platforms to support implementing and maintaining CI/CD pipelines, developing and deploying Microservices as containerization in the Kubernetes clusters.
}

%-----------EDUCATION-----------------
\section{Education}
\customcventry{Aug 2018 - Sep 2022}{}{Ho Chi Minh University of Technology}{Ho Chi Minh, Vietnam}{}{Falcuty of Computer Science of Engineering}{\textit{Bachenlor of Engineering} in Computer Engineering}


%-----------Certificates-----------------
\section{Licenses \& Certifications}
{\begin{itemize}[label=\textbullet]
      \item \textit{Ets} TOEIC for Reading-Listening skills with 640/990 scores. (Aug. 2022)
      \item \textit{Ets} TOEIC for Speaking-Writing skills with 200/400 scores. (Sep. 2022)
      \item Fundamentals of Action Learning from \textit{WIAL Vietnam}. (Oct. 2023)
  \end{itemize}}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DEK Technologies Vietnam}{Ho Chi Minh, Vietnam}
      {DevOps Engineer}{Feb 2022 - Present}
      \resumeItemListStart
        \resumeItem{CI/CD Pipeline Management}
          {Creation and maintenance of the \textbf{Argo Workflow} pipeline, streamlining development processes for enhanced efficiency.}
        \resumeItem{Automation Expertise}
          {Utilize \textbf{} scripts and \textbf{Python}, in conjunction with \textbf{Docker}, \textbf{Kubernetes}, \textbf{Helm}, and \textbf{Jfrog Artifactory}, to automate tasks seamlessly through the \textbf{Argo Workflow} CI pipeline.}
        \resumeItem{Deployment Management}
          {Proficiently work with \textbf{Argo CD} to deliver resources to designated locations, ensuring a smooth deployment process.}
        \resumeItem{Clusters management}
          {Use \textbf{Rancher} for effectively manage \textbf{Kubernetes} clusters.}
        \resumeItem{Unit Testing}
          {Employ \textbf{Python} and \textbf{Pytest} to write comprehensive unit test cases for Microservices developed using \textbf{Python}.}
        \resumeItem{Backend deveploment}
          {Develop Microservices nodes using \textbf{Python} that provide \textbf{RESTful APIs} to support for CI/CD pipelines.}
        \resumeItem{Task Management}
          {Efficiently manage daily tasks through \textbf{Jira} and follow \textbf{Agile} way of working, ensuring seamless coordination and prioritization.}
        \resumeItem{Collaborative Problem Resolution}
          {Proactively bring up ideas, and engage in discussions with team members to identify and resolve challenges.}
      \resumeItemListEnd

    \resumeSubheading
      {CloudNine: The Automation Software Company}{Ho Chi Minh, Vietnam}
      {Embedded Linux Intern}{Jun 2021 - September 2021}
      \resumeItemListStart
        \resumeItem{Unittest implementation}
          {Write unit test cases for C++ application using \textbf{CppTest} framework.}
        \resumeItem{GNU Make}
          {Write Makefile for compiling C++ application on Linux environment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Other Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Flashcard tracker}
      {An application built from Python and deployed in AWS ECS  that communicates with users in Telegram, helps to learn and remember vocabulary performed in Flashcard.}
    \resumeSubItem{Health and life service}
      {Service built from Python and deployed in AWS ECS reminds users about goals in the day and scheduler via WhatsApp.}
    \resumeSubItem{Autonomous robot in uncertain environments}
      {Autonomous robot has model Turtlebot3 burger that can determine obstacles and move throughout open points to go to goal.}
  \resumeSubHeadingListEnd

%-----------Certificates-----------------
\iffalse % Current in blocked
\section{Online Courses \& Certifications}
{\begin{itemize}[label=\textbullet]
      \item Introduction to Digital Marketing (Jan. 2023) - \underline{\color{blue}\href{https://google.com/}{SEMRUSH}}
      \item Career Essentials in Digital Marketing by LinkedIn (Aug. 2022) - \underline{\color{blue}\href{https://google.com/}{LinkedIn}}
      \item Visualization with Tableau (Feb. 2022) - \underline{\color{blue}\href{https://google.com/}{Coursera}}
      \item Foundations of Google Analytics  (Jun. 2021) - \underline{\color{blue}\href{https://google.com/}{Google, Coursera}}
     \item Google Analytics for Power Users (Jun. 2021) - \underline{\color{blue}\href{https://google.com/}{Google}}
       \item The Fundamentals of Digital Marketing, (Jul. 2019) - \underline{\color{blue}\href{https://google.com/}{Google}} 
  \end{itemize}}
\fi

%--------PROGRAMMING SKILLS------------
\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Programming Languages:} C, C++, Python, Bash}
\item {\textbf{Technologies:} AWS, Kubernetes, Docker, Helm, Rancher, Argo Workflows, Argo CD, Artifactory, Git}
\item {\textbf{Developing environments:} Linux, Windows}
\item {\textbf{Database:} MySQL, Microsoft SQL, Elasticsearch}
\item {\textbf{Data visualization:} Kibana, Matplotlib}
\item {\textbf{Communication Protocol:} RESTful API, MQTT, Kafka}
\item {\textbf{Soft Skills:} Presentation, Planning, Organized, Creative Problem-Solving, Teamwork, Active Listening, Adaptability}
\end{itemize}}

%--------Languages---------------
\section{Languages}
\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item \textbf{Vietnamese} [Native]
    \item {\textbf{English} [Intermediate] - B2++}
    \end{itemize}
\end{multicols}

%-------------------------------------------
\end{document}